\textls[-0]{\thetitle}

### 2023-03-19 canonicitymodel.tex
Phrasing.

Notice that
$\prod_{\goodSub{\cdot}{\gm}{\Gm}} \prod_{\gm' \in \Gmodel{\Glued{\Gm}}(\gm)}$
is part of $\GTy{\!}{\!}$, $\GTm{\!}{\!}$, and $\GSub{\!}{\!}$.
The interesting fact is that, given a pair of arbitrary $\goodSub{\cdot}{\gm}{\Gm}$
and $\gm' \in \Gmodel{\Glued{\Gm}}(\gm)$, we can consider $(\gm, \gm')$ as an
element of $\GSub{\Glued{\cdot}}{\Glued{\Gm}}$.
Thus, we consider the pair $(\gm,
\gm')$ as $\Glued{\gm} \in \GSub{\Glued{\cdot}}{\Glued{\Gm}}$.
% Note that, for arbitrary $\Glued{\Gm} \in \GCon{k}$, we can consider it as $\Glued{\gm}$ as an element of $\GSub{\Glued{\cdot}}{}$

@@

Now we can extend the model above to include \TT constructs.
%We still start with the judgments.
%Since linkage transformers are just syntactic sugar, we will not interpret it.
The key idea of this extension is similar to that of the syntactic translation:
we interpret linkage types using the canonicity model of sigma types (developed in the prior work).
We use the inductive facility of the meta\-logic to justify our W-types.

>>>>

Notice that
$\prod_{\goodSub{\cdot}{\gm}{\Gm}} \prod_{\gm' \in \Gmodel{\Glued{\Gm}}(\gm)}$
is part of $\GTy{\!}{\!}$, $\GTm{\!}{\!}$, and $\GSub{\!}{\!}$.
An interesting fact about them is : given a pair of arbitrary $\goodSub{\cdot}{\gm}{\Gm}$
and $\gm' \in \Gmodel{\Glued{\Gm}}(\gm)$, we can consider $(\gm, \gm')$ as an
element of $\GSub{\Glued{\cdot}}{\Glued{\Gm}}$.
Thus, we can consider the pair $(\gm,
\gm')$ as an element $\Glued{\gm} \in \GSub{\Glued{\cdot}}{\Glued{\Gm}}$.

@@

Now we can extend the model above to include \TT constructs.
%We still start with the judgments.
%Since linkage transformers are just syntactic sugar, we will not interpret it.
The key idea of this extension is similar to that of the syntactic translation:
we interpret linkage types using the canonicity model of sigma types (developed in the prior work).
We use the inductive facility of the ambient meta\-logic to justify our W-types.

### 2023-03-19 syn-translate.tex
Phrasing.

We omit validating the equational rules ($\beta$, $\eta$, and substitution) here.
However, when we mutually recursively define
$\denotesT{\goodSig{\Gamma}{\_}{n}}$, ${\Sigr{\Gamma}{n}{}} $, and
$\denotesT{\cP}$ above, we actually have to prove the substitution laws
$\sub{(\TyTkg{\lsig})}{\gm}\equiv \TyTkg{\sub{\lsig}{\gm}}$ and $\sub{(\Sigr{\Delta}{n}{})}{\gm}
\equiv \Sigr{\Gamma}{n}{}$ together. 
% The details (of all the equational rules) can be found in the appendices written in (pseudo-)Agda form. We encourage the reader to read that (pseudo-)Agda-style proof because it is more friendly to type theorists, easy to do type checking and
% validate the proof and it is clearer on the mathematical object each
% translation uses.

>>>>

We omit validating the equational rules ($\beta$, $\eta$, and substitution) here.
Note that, when we mutually recursively define the type
${\Sigr{\Gamma}{n}{}}$ (of signatures $\denotesT{\goodSig{\Gamma}{t}{n}}$), and the function
$\denotesT{\cP} = \mathscr{P}$ above, we actually have to prove the two substitution laws
$\sub{(\TyTkg{\lsig})}{\gm}\equiv \TyTkg{\sub{\lsig}{\gm}}$ and $\sub{(\Sigr{\Delta}{n}{})}{\gm}
\equiv \Sigr{\Gamma}{n}{}$ together. 
% The details (of all the equational rules) can be found in the appendices written in (pseudo-)Agda form. We encourage the reader to read that (pseudo-)Agda-style proof because it is more friendly to type theorists, easy to do type checking and
% validate the proof and it is clearer on the mathematical object each
% translation uses.
